---
title: "Assignment_1_Jessie Xu"
author: "Jessie Xu"
date: "2021/9/22"
output:
  pdf_document: default
  html_document: default
---

```{r}
library(tidyverse)
```
(1)After install the package once, we need to use library() to invoke the relative functions everytime we start our R.

(2)Using packman::p_load() can replace install.packages("A","B") and library(A,B) at the same time.

```{r}
# call built-in data mtcars.
data(mtcars)

# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]

# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]  
```
Pay attention to the expression of the questions, there are so many time that I read the question in reverse, like "reduce..to.." actually means reserve the things after "to". 

```{r}
# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)  

# Now use the function from hand_functions.R
sp_out <- sum_special(mtcars_mpg2)
sp_out 
```
(1)“echo=TRUE” means that all setted code chunks will be included in the final rendered version.

(2)Using the new "sum_special()" function, we can get the value of the mean, the var, the cov and the cor of our target variables.

```{r}
ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()
```

(1)"#B22222" is a great dark red shade.

(2)"span" controls the amount of smoothing for the default loess smoother. The larger the span the smoother the plot.

(3)The shade aroung the line means the confidence bands of the data.

(4)theme_minimal() means no context like no black grid lines and no dark gray color of the background.

```{r}
# draw a boxplot by using geom_boxplot()
ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")
```

```{r}
# install.packages("esquisse")
# library(esquisse)
# esquisser(data = mtcars_mpg2, viewer = "browser")

# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?
```

By running the code of line 58-60, I noticed that the presence or absence of "as.factor()" function can affect the graph we plot. So I try to generate a new colunm which add cyl as a classification variable.

```{r}
mtcars_mpg2$factor_cyl <- as.factor(mtcars_mpg2$cyl)
# esquisser(data = mtcars_mpg2, viewer = "browser")
```
Just drag "factor_cyl" into the X box and drag "mpg" in to y box, we can plot this boxplot made with esquisse() successfully. 


